Supplementary Information

### 2020-10-17 doc/manuscript/MEE_manuscript.Rmd
update word style

---
title: ''
output: word_document
bibliography: references.bib
csl: methods-in-ecology-and-evolution.csl

@@

### Abstract

@@

### Introduction

@@

### Materials and Methods

#### Data sources and preparation

@@

#### Analysis methods

@@

*Identifying key climate drivers*

@@

*Combining drivers in GLS model*

@@

### Results

*Identifying climate drivers*

@@

@@

@@

@@

### Discussion

@@

#### corroboration of insight from conventional methods
*( more objective approach to produce similar results to what has been shown using more conventional methods)*

#### new insight
*(could potentially provide new insight that would not be expected using more conventional methods.  It would be useful if there are examples from the analysis in this paper that could clearly illustrate new insight that would not have been found with conventional methods. )*

#### future challenges (?)
*(still face a problem when future climate is outside of the range of values used to model the climate-growth relationship. )*

@@

### Acknowledgements
Thanks to Pete Kerby-Miller for bark thickness data.
Helpful feedback was provided by Albert Kim...
This analysis was funded by a Smithsonian Scholarly Studies grant to KAT, SM, HCM, and CP.
The participation of PS, JK, and IV from the Czech Republic was supported by the Czech Science Foundation, project No. 19-09427S

### Authors' contributions
KAT, VH, CR, RA, CP conceived the ideas and designed methodology; 
[most authors] collected the data; 
VH, BG, EGA, and NP organized and analysed the data; 
KAT led the writing of the manuscript. 
All authors contributed critically to the drafts and gave final approval for publication.

### Data availability
```{r eval=FALSE, echo=FALSE}
# To enable readers to locate archived data from papers, we require that authors list the database and the respective accession numbers or DOIs for all data from the manuscript that has been made publicly available.
```

@@

### References

>>>>

---
title: ''
output: 
    bookdown::word_document2: 
      reference_docx: word-styles-reference.docx #make sure this line is indented! see this guide for formatting: https://rmarkdown.rstudio.com/articles_docx.html
bibliography: references.bib
csl: methods-in-ecology-and-evolution.csl

@@

# Abstract

@@

# Introduction

@@

# Materials and Methods

## Data sources and preparation

@@

## Analysis methods

@@

### Identifying key climate drivers

@@

### Combining drivers in GLS model

@@

# Results

### Identifying climate drivers

@@

### Climate sensitivity

@@

### Influence of DBH

@@

### Additive and interactive effects of climate and DBH

@@

# Discussion

@@

## corroboration of insight from conventional methods
*( more objective approach to produce similar results to what has been shown using more conventional methods)*

## new insight
*(could potentially provide new insight that would not be expected using more conventional methods.  It would be useful if there are examples from the analysis in this paper that could clearly illustrate new insight that would not have been found with conventional methods. )*

## future challenges (?)
*(still face a problem when future climate is outside of the range of values used to model the climate-growth relationship. )*

@@

# Acknowledgements
Thanks to Pete Kerby-Miller for bark thickness data.
Helpful feedback was provided by Albert Kim...
This analysis was funded by a Smithsonian Scholarly Studies grant to KAT, SM, HCM, and CP.
The participation of PS, JK, and IV from the Czech Republic was supported by the Czech Science Foundation, project No. 19-09427S

# Authors' contributions
KAT, VH, CR, RA, CP conceived the ideas and designed methodology; 
[most authors] collected the data; 
VH, BG, EGA, and NP organized and analysed the data; 
KAT led the writing of the manuscript. 
All authors contributed critically to the drafts and gave final approval for publication.

# Data availability
```{r eval=FALSE, echo=FALSE}
# To enable readers to locate archived data from papers, we require that authors list the database and the respective accession numbers or DOIs for all data from the manuscript that has been made publicly available.
```

@@

# References
